---
title: "Week2 Interactive Mapping Assignment"
author: "Ken"
date: "April 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## R Markdown and Leaflet Instructions

"Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!"


## Submission

Use publicly available child care data to map the licensed and registered Child Care providers of Detroit, Michigan.

```{r, echo=FALSE, warning=FALSE}
library(leaflet); library(ggmap)
detroit <- read.csv(file = "D:/Data Products/Detroit Child Care Providers (April 2018) v2.csv", header = TRUE)

careLatLong <- data.frame(
  lat = detroit$LAT,
  lng = detroit$LONG
)

careIcons <- makeIcon(
  iconUrl = "http://www.greatstarttoquality.org/sites/all/themes/ecic/logo.png",
  iconWidth = 35*215/230, iconHeight = 35,
  iconAnchorX = 35*215/230, iconAnchorY = 35
)

careSites <- paste("License Number: ", detroit$License, " <br>", "Facility Name: ", detroit$Facility, " <br>", "Address: ", detroit$Address)

```


## April 9, 2018

GitHub wouldn't host an interactive HTML document with as much data as I intended to use so I reduced it to 100 cases.

```{r, echo=FALSE, warning=FALSE} 
careLatLong %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon=careIcons, popup = careSites) %>%
  setMaxBounds(lng1 = -82, lat1 = 42, lng2 = -84, lat2 = 43) %>%
  setView(lng = mean(detroit$LONG), lat = mean(detroit$LAT), zoom = 11)

```

